### 2021-03-12 results/draft.tex
added a ref. into Intro

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
Field surveys using environmental DNA (eDNA) are widely used for monitoring such as endangered species, invasive species, and biodiversity 
%detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
because the surveys of eDNA are easy to detect occurrence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015). %Dorazioに引用されていたやつ．あとで再確認
However, uncertainty of the occurrence of eDNA is a issue in eDNA studies because various factors, such as biological and environmental features, intricately affect the shedding (i.e., production of eDNA from organisms) and degradation (i.e., decay of eDNA from a system) of eDNA (Fig. 1). Therefore, it is necessary to consider the spatial uncertainty included in eDNA to infer the spatial distribution of species from eDNA occurrence data.

>>>>

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
Field surveys using environmental DNA (eDNA) are widely used for monitoring such as endangered species, invasive species (e.g., Dougherty et al. 2016%ザリガニJ appl ecol
; Larson et al. 2020%レビュー
), and biodiversity 
%detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
because the surveys of eDNA are easy to detect occurrence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015). %Dorazioに引用されていたやつ．あとで再確認
However, uncertainty of the occurrence of eDNA is a issue in eDNA studies because various factors, such as biological and environmental features, intricately affect the shedding (i.e., production of eDNA from organisms) and degradation (i.e., decay of eDNA from a system) of eDNA (Fig. 1). Therefore, it is necessary to consider the spatial uncertainty included in eDNA to infer the spatial distribution of species from eDNA occurrence data.
